\documentclass[12pt,letterpaper]{hmcpset}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}

% info for header block in upper right hand corner
\name{Box#: \underline{\hspace{1cm}}(Name On Back)}
\class{Math 60: Section \underline{\hspace{1cm}}}
\assignment{Assignment 3}
\duedate{Due Date: 9/28/18}

\begin{document}

\problemlist{Section 3.1: 10, 17\\ Section 3.2: 1, 4, 13\\ Section 3.3: 24\\ Section 3.4: 4, 7, 12, 23}

\begin{problem}
Section 3.1\\
\textit{Calculate the velocity, speed, and acceleration of the paths
given in Exercises 7-10.}\\
10. $\mathbf{x}(t) = (e^t , e^{2t} , 2e^t )$
\end{problem}
\newpage

\begin{problem}
\textit{In Exercises 15-18, find an equation for the line tangent to the
given path at the indicated value for the parameter.}\\
17. $\mathbf{x}(t) = (t^2, t^3, t^5), t = 2$
\end{problem}
\newpage


\begin{problem}
Section 3.2\\
\textit{Calculate the length of each of the paths given in Exercises
1-6.}\\
1. $\mathbf{x}(t) = (2t + 1, 7 - 3t), -1 \leq t \leq 2$
\end{problem}
\newpage


\begin{problem}
\textit{Calculate the length of each of the paths given in Exercises
1-6.}\\
4. $\mathbf{x}(t) = 7\mathbf{i} + t\mathbf{j} + t^2 \mathbf{k}, 1 \leq t \leq 3$
\end{problem}
\newpage


\begin{problem}
13. This problem concerns the path $\mathbf{x} = |t - 1| \mathbf{i} + |t| \mathbf{j}, 
−2 \leq t \leq 2$.
\begin{enumerate}
    \item[(a)]Sketch this path.
    \item[(b)]The path fails to be of class $C^1$ but is piecewise $C^1$. Explain.
    \item[(c)]Calculate the length of the path.
\end{enumerate}
\end{problem}
\newpage


\begin{problem}
Section 3.3\\
24. Consider the vector field $\mathbf{F} = 2x\mathbf{i} + 2y\mathbf{j} - 3\mathbf{k}$.
\begin{enumerate}
    \item[(a)]Show that \textbf{F} is a gradient field. 
    \item[(b)]Describe the equipotential surfaces of \textbf{F} in words and with sketches.
\end{enumerate}
\end{problem}
\newpage


\begin{problem}
Section 3.4\\
\textit{Calculate the divergence of the vector fields given in Exercises 1-6.}\\
4. $\mathbf{F}= z \cos (e^{y^2}) \mathbf{i} + x\sqrt{z^2 + 1} \mathbf{j} + e^{2y} \sin (3x) \mathbf{k}$
\end{problem}
\newpage


\begin{problem}
\textit{Find the curl of the vector fields given in Exercises 7-11.}\\
7. $\mathbf{F} = x^2\mathbf{i} − xe^y\mathbf{j} + 2xyz\mathrm{k}$
\end{problem}
\newpage


\begin{problem}
12.
\begin{enumerate}
    \item[(a)]Consider again the vector field in Exercise 8 and its curl. Sketch the vector field and use your picture to explain geometrically why the curl is as you calculated.
    \item[(b)] Use geometry to determine $\nabla \times \mathbf{F}$, where $\mathbf{F}=\frac{(x\mathbf{i}+y\mathbf{j}+z\mathbf{k})}{\sqrt{x^2+y^2+z^2}}$.
    \item[(c)] For \textbf{F} as in part (b), verify your intuition by explicitly computing $\nabla \times \mathbf{F}$
\end{enumerate}
\end{problem}
\newpage


\begin{problem}
\textit{In Exercises 21-25, establish the given identities. (You may assume that any functions and vector fields are appropriately differentiable.)}\\
23.$\nabla \cdot (f\mathbf{F})=f\nabla \cdot \mathbf{F} + \mathbf{F} \cdot \nabla f$ 
\end{problem}

%\begin{solution}
%\end{solution}

% Add pairs of problems and solutions as needed

\end{document}
